Hector Permafrost

### 2019-02-06 analysis/paper/paper.Rmd
Add permafrost emissions cases to paper outline

>>>>

Default heterotrophic respiration ($R$) scheme for a pool $p$ (detritus or soil) in Hector:

$$ R_{p} = C_p \times f_p \times Q_{10} ^ \frac{T}{10} $$

This is case 1.

Case 2 uses the same formulation, but splits permafrost C into its own "biome", with its own photosynthesis ($\Beta$) and respiration ($Q_{10}$) parameters.

Case 3 extends Case 2 by calculating CO~2~ and CH~4~ emissions as a fraction of the total respiration, controlled by two new parameters $\alpha$ and $\phi$:

$$ R_{p,tot} = C_p \times f_p \times Q_{10} ^ \frac{T}{10} $$

$$ R_{p, CH_4} = \alpha R_{p, tot} $$

$$ R_{p, CO_2} = (1 - \alpha) ^ \phi R_{p, tot} $$

## Other notes
